full title

### 2020-11-20 paper/pldi21/related.tex
Revised Sec. 7

\section{Related Work}\label{sec:related}

Several researchers have introduced analysis technique to utilize dynamic
analysis for static analysis in three different ways: combined analysis,
automatic modeling, and pruning states.

\paragraph{Combined Analysis}

The most related previous work is the combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.  They
proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach have several
limitations compared to the dynamic shortcut.  First, they syntactically divides
a given program to \textit{applications} parts for static analysis and
\textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switching between static and dynamic and even impossible to perform both
of static and dynamic analysis to the same program part in different contexts.
Besides, they introduced \textit{mostly-concrete interpretation} similar with
our sealed symbolic execution.  However, it supports only a special
\textit{unknown} value that represents any possible value.  Thus, it cannot
preserves the precision of complex abstract domains~\cite{safe, tajs, regex,
weaklySPE} frequently used in JavaScript static analysis.  In the other hand,
the sealed symbolic execution automatically detects whether the abstract
semantics for abstract values.  Finally, \concerto preserves the soundness when
the program satisfies the \textit{state separation hypothesis}.  They assume
that states of application and framework parts do not interrogated or
manipulated by each other.  While it is reasonable for static analysis of Java
applications using external libraries, the assumption is not satisfied for
JavaScript programs in general.  Unlike their approach, our approach does not
have any assumption between static and dynamic analysis parts.

\paragraph{Automatic Modeling}
For static analysis of JavaScript programs, modeling behaviors of built-in
libraries or host-dependent functions is required because they are opaque
codes.  Since manual modeling is error-prone, tedious, and labor-intensive,
several researchers~\cite{safewapi, safets} utilize type information to
automatically model their behaviors.  However, type information is too imprecise
to reflect the detailed semantics and is difficult to represent the
side-effects.  To alleviate the problem, \citet{mimic} introduced the technique
to infer JavaScript codes for opaque codes using concrete execution.  They
captured the effects of opaque codes on user objects by collecting partial
execution traces and synthesized JavaScript codes based on the extracted
behaviors.  They also leveraged ES6 \jscode{Proxy} objects to capture the
effects on user objects.  Instead of synthesizing JavaScript codes,
\citet{opaque-model} presented a \textit{Sample-Run-Abstract (SRA)} approach for
on-demand modeling thus they focused on the current abstract state during static
analysis.  It first \textit{samples} concrete states in a well-distributed way,
\textit{runs} each sampled state on a JavaScript engine, and \textit{abstract}
executions results.  However, all of previous works sacrifice the soundness of
static analysis.  On the other hand, while the dynamic shortcut is not
applicable for all invocation of opaque functions, it is sound if it is
applicable.

\paragraph{Pruning Analysis Scopes}
Another approach to utilize dynamic analysis for JavaScript static analysis is
to prune the scope of analysis.  \citet{blended} introduced \textit{blended
taint analysis} that specializes JavaScript dynamic language features such as
dynamic code generation (e.g. \jscode{eval}) or variadic function calls.  They
first performs dynamic analysis to collect traces with concrete values used in
dynamic language features and restrict the semantics of features based on the
collected traces during static analysis.  \citet{battles, eha} utilizes three
different points to reduce analysis scopes: initial states, dynamically loaded
files, and event handlers.  They dumped the initial states from a specific web
browser to focus on analyzing the behaviors of web browsers running on the
browser.  Then, they collected paths of dynamically loaded files via concrete
executions and utilized the path information in static analysis.  For event
handlers, they intentionally analyzed partial execution flows using concrete
user events.  They collected concrete states for each entry of event handler
during dynamic analysis, merged them to a single abstract state, and analyzed
the event handler with the abstract state.  Unfortunately, all of them does not
preserve soundness of static analysis unlike the dynamic shortcut.

>>>>

\section{Related Work}\label{sec:related}
Researchers have introduced various analysis technique to utilize dynamic
analysis for static analysis in three ways: combined analysis,
automatic modeling, and pruning analysis scope.

\paragraph{Combined Analysis}
The most related previous work is combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.
They proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach has several
limitations compared with dynamic shortcuts.  First, it syntactically
divides a given program to \textit{applications} parts for static
analysis and \textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switch between static analysis and dynamic analysis.  It is
even impossible to perform both static and dynamic analysis of 
the same program part in different contexts.  In addition, while they
introduced \textit{mostly-concrete interpretation} similar to our
sealed symbolic execution, it supports only a special \textit{unknown}
value that represents any possible value.  Thus, it cannot preserve
the precision of complex abstract domains~\cite{revisit-recency,
  regex, weaklySPE} frequently used in JavaScript static analysis.
On the contrary, sealed symbolic execution automatically detects when
to switch to static analysis to use abstract semantics for abstract values.
Finally, \concerto preserves the soundness when a program satisfies
the \textit{state separation hypothesis}.  It assumes that the states
of application parts and framework parts are not interrogated
or manipulated by each other.  While the assumption may be reasonable
for static analysis of Java applications using external libraries, it
is not satisfied for JavaScript programs in general.  Unlike their
approach, our approach does not have any assumptions between static and
dynamic analysis parts.

\paragraph{Automatic Modeling}
For static analysis of JavaScript programs, modeling behaviors of built-in
libraries or host-dependent functions is necessary because they are opaque code.
Since manual modeling is error-prone, tedious, and labor-intensive,
researchers~\cite{safewapi, safets} have utilized type information to
automatically model their behaviors.  However, type information is too imprecise
to reflect complex semantics and is difficult to represent the side-effects.
To alleviate the problem, \citet{mimic} introduced a technique
to infer JavaScript code for opaque code using concrete execution.
They captured the effects of opaque code on user objects by collecting partial
execution traces and synthesized JavaScript code using the extracted behaviors.
They also leveraged ES6 \jscode{Proxy} objects to capture the effects on user objects.
Instead of synthesizing JavaScript code,
\citet{opaque-model} presented a \textit{Sample-Run-Abstract (SRA)} approach for
on-demand modeling focusing on the current abstract states during static analysis.
It first \textit{samples} concrete states in a well-distributed manner,
\textit{runs} each sampled state on a JavaScript engine, and \textit{abstracts} execution results.
However, all the previous work sacrifice the soundness of static analysis.
On the contrary, while dynamic shortcuts may not be applicable to some
invocations of opaque functions, it is sound if it is applicable.

\paragraph{Pruning Analysis Scope}
Another approach to utilize dynamic analysis for JavaScript static analysis is
to prune the scope of analysis.  \citet{determinacy} proposed dynamic
determinacy analysis, which infers determinacy facts like whether a
variable or an expression at a given location holds the same value in
all possible execution of a program via concrete execution.
They specialized target source code with determinacy
facts so that static analysis can get benefits from elimination of dynamic code
generation such as \jscode{eval} and constant property names.
\citet{blended} introduced \textit{blended taint analysis}, which specializes JavaScript dynamic
language features such as dynamic code generation or variadic function calls.
It first performs dynamic analysis to collect traces with concrete values used
in dynamic language features and restricts the semantics of features based on the
collected traces during static analysis.  \citet{battles, eha} utilize three different points to reduce
analysis scope: initial states, dynamically loaded files, and event handlers.
They dumped the initial states from a specific web browser to focus on
analysis of the behaviors of web applications running on the browser.
Then, they collected paths of dynamically loaded files via concrete
execution and utilized the path information in static analysis.
For event handlers, they intentionally analyzed partial execution flows using concrete user events.
They collected concrete states for each entry of an event handler
during dynamic analysis, merged them to a single abstract state, and analyzed
the event handler with the abstract state.
Unfortunately, all the above mentioned approaches do not preserve
soundness of static analysis unlike our approach using dynamic shortcuts.
